Welfare Expectations Across U.S. Economic Cycles

### 2024-04-24 paper/paper.qmd
Update figure 1
Update caption for figures

In this model, proportion\_too\_little_i indicates the predicted proportion of "too little" responses for the i^{th} year, $\beta_0$ represents the model's intercept—the starting point on the y-axis when the year is zero, which we interpret as the survey's baseline year of 1972. The coefficient $\beta_1$ indicates the amount of change in "Too Little" responses we can expect with each passing year. If $\beta_1$ is positive, it supports our hypothesis of an upward trend.

@@

### Interpretation of the Trend
The slight upward trajectory observed in the model output [@tbl-linear-trend] can be interpreted as a growing public sentiment that welfare provision is "too little." This might reflect an overall increase in public expectations for welfare support, possibly driven by social, economic, or policy changes over time. The pattern could also indicate a responsiveness to economic conditions, with higher "Too Little" responses potentially following economic downturns.

@@

```{r}
#| warning: false
#| tbl-cap: Linear model showing the trend of Too Little responses
#| label: tbl-linear-model
#| message: false
#| echo: false
#| eval: true

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tbl-linear-trend
#| tbl-cap: The model trend of Too Little responses is increasing every years

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-linear-trend
#| fig-cap: The trend of Too Little responses is increasing every years
# Visualizing the trend
ggplot(model_data, aes(x = year, y = proportion_too_little)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  labs(x = "Year",
       y = "Proportion of 'Too Little' Responses") +
  theme_minimal()
```

@@

```{r}
#| warning: false
#| fig-cap: Comparison between 1980 and 1982, 2018 and 2021
#| label: fig-comparison-years
#| message: false
#| echo: false

@@

## Trends in 'Too Much' Responses

@@

```{r}
#| warning: false
#| fig-cap: There are major social events in some missing years 
#| label: fig-missing-years
#| message: false
#| echo: false

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Annual trends show inconsistent total response rates
#| label: fig-trends-response

@@

Overall the model's predictive power is limited to the data range from 1972 to 2022. It may not accurately forecast future trends, especially in the face of unprecedented events such as the COVID-19 pandemic. The 2021 spike in "Too Little" responses could be an outlier due to the pandemic's unique economic impact, which a model based on past data might not predict accurately.

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

## Diagnostics
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

>>>>

In this model, proportion\_too\_little_i indicates the predicted proportion of "too little" responses for the i^{th} year, $\beta_0$ represents the model's intercept—the starting point on the y-axis when the year is zero, which we interpret as the survey's baseline year of 1972. The coefficient $\beta_1$ indicates the amount of change in "too little" responses we can expect with each passing year. If $\beta_1$ is positive, it supports our hypothesis of an upward trend.

@@

### Interpretation of the Trend
The slight upward trajectory observed in the model output [@tbl-linear-trend] can be interpreted as a growing public sentiment that welfare provision is "too little." This might reflect an overall increase in public expectations for welfare support, possibly driven by social, economic, or policy changes over time. The pattern could also indicate a responsiveness to economic conditions, with higher "too little" responses potentially following economic downturns.

@@

```{r}
#| warning: false
#| tbl-cap: Linear Model Showing the Trend of Too Little Responses
#| label: tbl-linear-model
#| message: false
#| echo: false
#| eval: true

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tbl-linear-trend
#| tbl-cap: The Model Trend of Too Little Responses is Increasing Every Year

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-linear-trend
#| fig-cap: The Trend of Too Little Responses is Increasing Every Year
# Visualizing the trend
ggplot(model_data, aes(x = year, y = proportion_too_little)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  labs(x = "Year",
       y = "Proportion of 'Too Little' Responses") +
  theme_minimal()
```

@@

```{r}
#| warning: false
#| fig-cap: Comparison Between 1980 and 1982, 2018 and 2021
#| label: fig-comparison-years
#| message: false
#| echo: false

@@

## Trends in Too Much Responses

@@

```{r}
#| warning: false
#| fig-cap: There are Major Social Events in Some Missing Years 
#| label: fig-missing-years
#| message: false
#| echo: false

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Annual Trends Show Inconsistent Total Response Rates
#| label: fig-trends-response

@@

Overall the model's predictive power is limited to the data range from 1972 to 2022. It may not accurately forecast future trends, especially in the face of unprecedented events such as the COVID-19 pandemic. The 2021 spike in "too little" responses could be an outlier due to the pandemic's unique economic impact, which a model based on past data might not predict accurately.

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining How the Model Fits, and is Affected by, the Data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

## Diagnostics
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the Convergence of the MCMC Algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2
